Figure Extra

### 2022-09-05 Figures/Figures_nonTCGA.Rmd
add TIL10 and CCLE_TIL10 signatures to Non TCGA
validated by hand

# GSE72056
## Data loading
```{r}
deconv_GSE72056 <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #! fix naming of deconv results

@@

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_GSE72056 <- list()
dict_GSE72056[["BPRNACan"]] <- list(B = c("B"),
                                     CAFs = c(),
                                     CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("M0", "M1", "M2"),
                                     NK = c("NK"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c("cancer"),
                                     Other = c("Mono", "Neu"))

@@

# dict_GSE72056[["CCLE_TIL10"]] <- list(B = c(),
#                                      CAFs = c(),
#                                      CD4 = c(),
#                                      CD8 = c(),
#                                      Endothelial = c(),
#                                      Macrophages = c(),
#                                      NK = c(),
#                                      Th = c(),
#                                      Treg = c(),
#                                      Cancer = c(),
#                                      Other = c())

>>>>

# GSE72056
## Data loading
```{r}
deconv_GSE72056 <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_not_metastatic.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #! fix naming of deconv results

@@

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
## validated by jacobo 05/09/2022

dict_GSE72056 <- list()
dict_GSE72056[["BPRNACan"]] <- list(B = c("B"),
                                     CAFs = c(),
                                     CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("M0", "M1", "M2"),
                                     NK = c("NK"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c("cancer"),
                                     Other = c("Mono", "Neu"))

@@

dict_GSE72056[["TIL10"]] <- list(B = c("B.cells"),
                                     CAFs = c(),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("Macrophages.M1", "Macrophages.M2"),
                                     NK = c("NK.cells"),
                                     Th = c(),
                                     Treg = c("Tregs"),
                                     Cancer = c(),
                                     Other = c("Monocytes", "Neutrophils", "Dendritic.cells"))

dict_GSE72056[["CCLE_TIL10"]] <- list(B = c("B.cells"),
                                     CAFs = c(),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("Macrophages.M1", "Macrophages.M2"),
                                     NK = c("NK.cells"),
                                     Th = c(),
                                     Treg = c("Tregs"),
                                     Cancer = c("Cancer.cells"), #the only diff respect Til10
                                     Other = c("Monocytes", "Neutrophils", "Dendritic.cells"))

dict_GSE72056[["CD226"]] <- list(B = c("B"),
                                     CAFs = c(),
                                     CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("M1", "M2"),
                                     NK = c("NK"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c(),
                                     Other = c("Mono", "Neu"))
